Automatic discovery of cell types and microcircuitry from neural connectomics

### 2014-06-17 docs/paper.tex
text updates etc

%\documentclass{nature}
\documentclass{article}
\usepackage[english,american]{babel}
\usepackage[backend=biber,style=nature]{biblatex}
\usepackage[disable]{todonotes}
\usepackage{grffile}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{fullpage}
%\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage{amsmath}
%\usepackage{subcaption}
%\usepackage{multicol}
\usepackage{csquotes}
\usepackage{pdfpages}
\usepackage{placeins}

@@

The discovery of structure is a crucial aspect of network
science. Early approaches focused on global graph properties, such as
the types of scaling present in the network \autocite
{WattsStrogatz1998}.  While this approach leads to an understanding
of the global network, more recent work aims at identifying very small-scale
repeat patterns, or “motifs” in networks\autocite{Milo2002}. \todo{motifs vs type}.

@@

We can thus evaluate our model along three sets of parameters: how
closely does our clustering agree with neuroanatomists' knowledge? 
Given two cells, how accurately can our model predict the link
between them? And how closely does the spatial extent (within a layer)
of our identified types agree with the known neuroanatomists.

>>>>

%\documentclass{nature}
\documentclass{article}
\usepackage[english,american]{babel}
\usepackage[backend=biber,style=nature]{biblatex}
\usepackage{todonotes}
\usepackage{grffile}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{fullpage}
%\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage{amsmath}
%\usepackage{subcaption}
%\usepackage{multicol}
\usepackage{csquotes}
\usepackage{pdfpages}
\usepackage{placeins}

@@

The discovery of structure is a crucial aspect of network
science. Early approaches focused on global graph properties, such as
the types of scaling present in the network \autocite
{WattsStrogatz1998}.  While this approach leads to an understanding
of the global network, more recent work aims at identifying very small-scale
repeat patterns, or “motifs” in networks\autocite{Milo2002}. These motifs
are defined not between different node types, but rather represent repeated
patterns of topology.

@@

We evaluate our model along three sets of parameters: how
closely does our clustering agree with neuroanatomists' knowledge? 
Given two cells, how accurately can our model predict the link
between them? And how closely does the spatial extent (within a layer)
of our identified types agree with the known neuroanatomists.
